Stack Safety as a Security Property

### 2020-07-08 main.tex
Nit

\section{Stack Safety and Unsafety by Example}
\label{sec:running-example}

We begin with a running example that will serve both to concretely
demonstrate the ``stack-unsafe'' behaviours we intend to preclude and to
ground and illustrate the formal properties and enforcement mechanisms in
later sections.

>>>>

\section{Stack {\underline{Un}}safety by Example}
\label{sec:running-example}

We begin with a running example that will serve both to demonstrate several
``stack-unsafe'' behaviours that our stack safety property should prohibit
and to ground the technical presentation in later sections.
